VM-Centric Snapshot Deduplication for Cloud Data Backup

### 2015-03-10 snapshot_system/mass_background.tex
re

While deduplication reduces storage cost, it creates an artificial data dependence among VMs: when a shared data chunk
is lost in the storage, all VMs that refer such chunks after deduplication face a data loss.
The work in ~\cite{Reliability06} identifies such an issue in file systems 
and uses more replication for data shared by more files,
and we will adopt this idea.
When the backup storage is implemented using a distributed file system such as Hadoop and 
Google file system~\cite{googlefs03},  
the file system block  size is often chosen to be large (e.g. 64MB). On the other hand, 
deduplication implementations~\cite{Guo2011,extreme_binning09,bottleneck08,Jin2009,Dong2011}
 typically use smaller chunk sizes (e.g. 4K bytes).
Thus we need to address  the size gap between file system blocks and chunks.  
%in adding more replications for popular chunks.

>>>>

While deduplication reduces storage cost, it creates an artificial data dependence among VMs: when a shared data chunk
is lost in the storage, all VMs that refer such chunks after deduplication face a data loss.
The work in ~\cite{Reliability06} identifies such an issue in file systems 
and uses more replication for data shared by more files,
and we follow this idea and study VM-centric strategies.
When the backup storage is implemented using a distributed file system such as Hadoop and 
Google file system~\cite{googlefs03},  
the file system block  size is often chosen to be large (e.g. 64MB). On the other hand, 
deduplication implementations~\cite{Guo2011,extreme_binning09,bottleneck08,Jin2009,Dong2011}
 typically use smaller chunk sizes (e.g. 4K bytes).
Thus we need to address  the size gap between file system blocks and chunks.  
%in adding more replications for popular chunks.

### 2015-03-10 snapshot_system/mass_dedupanalysis.tex
re

\section{Impact on Deduplication Efficiency}
Choosing the top $k$ value  for the most popular chunks affects the deduplication efficiency.
We analyze this impact based on the characteristics  of the VM snapshot traces
studied from  application datasets.
A previous study shows that the popularity of data chunks after local deduplication follows 
a Zipf-like distribution\cite{Breslau1999a} and its
exponent $\alpha$ is ranged between 0.65  and  0.7~\cite{WeiZhangIEEE}. 
%Figure~\ref{fig:Datazipf} illustrates the Zipf-like distribution of chunk popularity.
The parameters we will use in our analysis below are defined in
Table~\ref{tab:symbol}.

>>>>

\section{Impact of Top $k$ Value on Deduplication Efficiency}
\label{sect:dedupanalysis}

Choosing the top $k$ value  for the most popular chunks affects the deduplication efficiency.
We analyze this impact based on the characteristics  of the VM snapshot traces
studied from  application datasets.
A previous study shows that the popularity of data chunks after local deduplication follows 
a Zipf-like distribution\cite{Breslau1999a} and its
exponent $\alpha$ is ranged between 0.65  and  0.7~\cite{WeiZhangIEEE}. 
%Figure~\ref{fig:Datazipf} illustrates the Zipf-like distribution of chunk popularity.
Additional parameters used in this analysis are defined in Table~\ref{tab:symbol2}.

\begin{table}[htbp]
%\begin{table}[t]
\small
\centering
%\tabcolsep=0.11cm
\begin{tabular}{|p{1.0cm}|p{5.75cm}|}
\hline
$k$ &  the number of top most popular chunks selected for deduplication\\ 
\hline
$c$ &  the total amount of data chunks in a cluster of VMs\\ 
\hline
$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
\hline
$f_i$ &  the frequency for the $i$th most popular fingerprint\\
\hline
$\delta$ &  the percentage of duplicates detected in local deduplication\\
\hline
$\sigma$ & = percentage of unique data  belonging to  PDS\\
%\hline
%$V$ & the average number of VMs per machine\\
\hline
%$E_c, E_o$ & deduplication efficiency of VC and VO \\
%\hline
%$D$ & the amount of unique data on each machine\\
%\hline
%$s$ & the average data chunk size. Our setting is  4K.\\
%\hline
%$s$ & the average number of chunks per FSB\\
%\hline
%$m$ & memory size on each node used by VC\\ 
%\hline
%$E$ & the size of an popular data index entry\\
%\hline
%$N_1$, $N_2$ & the average no.  of non-PDS and PDS file blocks in a VM in VC\\
%\hline
%$N_o$, $V_o$ & the average no.  of file blocks  in a VM and the average no. of VMs shared by a file system block in VO\\
%\hline
%A(r) & availability of a file block with $r$ replicas and $d$ failed physical machines\\
%\hline
\end{tabular}
\caption{Parameters for modeling deduplication.}
%\caption{Parameters for modeling deduplication with top $k$ popular chunks.}
\label{tab:symbol2}
\end{table}

### 2015-03-10 snapshot_system/mass_eval.tex
prepare for mass conference
re

\comments{
old table, delete 4%
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline 
&
     \multicolumn{4}{|c|}{VC}  & VO \\ \hline
&
     2\%PDS  &  No PDS &2\%PDS     & 4\%PDS & SRB  \\ 
&     no-simi&   &&  &    \\ \hline
Dedup &     94.31\%& 93.02\%  & 96.01\% & 96.58\% & 97.86\% \\ \hline
Mem(MB) &     108&  46 & 118  & 190 & 2400 \\ \hline
    \end{tabular}

}
\begin{table}[htb]
\centering
    \begin{tabular}{|c|c|c|c|c|}
    \hline 
&
     \multicolumn{3}{|c|}{VC}  & VO \\ \hline
&
     2\%No PDS &2\%PDS     & 2\%PDS & SRB  \\ 
&        &&     no-simi & \\ \hline
Dedup &      93.02\%  & 96.01\% & 94.31\% & 97.86\% \\ 
Efficiency &          &       &           &      \\    \hline 
Memory &      10MB & 118MB  & 108MB & 2.4GB \\ 
per-machine &      &   &  &  \\ \hline
    \end{tabular}
    \caption{Deduplication efficiency and per-machine memory usage for different VC settings and
        SRB.}
    \label{tab:efficiency-comparison}
\end{table}

Table~\ref{tab:efficiency-comparison} shows the deduplication efficiency and per-machine memory usage for SRB and VC with different 
settings.
% <<<<<<< HEAD
% Our deduplication efficiency is defined as the percent of duplicate chunks
% which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
% The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
% is defined in Table~\ref{tab:symbol}. 
% =======
Deduplication efficiency is defined as the percent of duplicate 
chunks removed, comparing to a perfect scheme which detects and removes  all duplicates. 
% so only global perfect deduplication can have 100\% efficiency.
% We also compare several PDS sizes chosen for VC.
%(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
Notice $\sigma$ is the percentage of unique chunks selected in PDS.
With $\sigma =2\%$, Column 3 shows its 
%memory usage for PDS index lookup per machine is about 100MB per machine and  the 
deduplication efficiency can 
reach over 96\%. 
%When $\sigma=4\%$, Column 4 shows that the deduplication efficiency can reach 96.6\% while 
%more index space is allocated  per machine for  PDS fingerprint lookup.
The loss of efficiency in VC is caused by the restriction of the physical memory available
in the cluster for fast in-memory PDS index lookup. 
Memory usage per machine is low because each machine only hosts $1/p$  of  index for PDS 
plus some buffer space where $p$ is the number of physical machines. 
%In the extreme case if we put all the fingerprint into PDS 
%index ($\sigma=100\%$) then VC will have 100\% efficiency.
SRB in Column 5 can deliver up to 97.86\% deduplication efficiency, which is slightly better than VC.
Thus this represents a tradeoff as VC uses much less resource  and faster deletion.
%with a slight reduction in deduplication efficiency.
Memory usage per machine in SRB includes the Bloom filter space to access the on-disk index
and  cache for frequently or recently accessed chunk index.  
% SRB can deliver up to 97.935\% deduplication efficiency which is slightly better than VC.
% Thus this represents a tradeoff: VC provides better fault tolerance and fast
% approximate deletion with competitive (but slightly lower) deduplication
% efficiency.
% >>>>>>> 4dcd68612b052c0f890ed30361a9ed03771b5df1
%its loss of efficiency is caused by the routing of data chunks which restricts the search scope
%of duplicate detection.
%SRB provides slightly better deduplication efficiency than our VC approach, which we accept
%because we are rewarded by architecture-wise benefits such as fault-tolerance and fast 
%Though not our primary goal, this result does show that VC can remove competitive amount of duplicates.

Column 2 of Table~\ref{tab:efficiency-comparison} shows deduplication efficiency of VC without 
using PDS and it achieves 93.02\% and  missed duplicates take  up-to  3.56\% of the original space, which
is about 356GB per physical machine. 
Column 4 of Table~\ref{tab:efficiency-comparison} shows deduplication efficiency of VC which only uses
the same offset in the parent segment to look for duplicates  but does not look for other potentially
similar segments. 
%There is a big efficiency drop in this curve when the number of VMs is about 30.
We explain why similarity-guided local search provides such an improvement as follows.
%Without this (i.e. when we only 
There are VMs in which data  segments are moved to another location on disk, for example 
when a file is rewritten
rather than modified in place,  
and a dirty-bit or offset-only based detection would not be able to detect such a movement.
We have found that in
approximately 1/3 of the VMs in our dataset this movement happens frequently.
In general, adding local similarity-guided search increases deduplication efficiency from 94\% to over 96\%.
That is one significant improvement compared to the work in ~\cite{WeiZhangIEEE}
which uses the parent segment at the same offset to detect duplicates instead of similarity-guided search.
% In general, our experiments show that
% dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
% which leads about a 75.86\% reduction.
% Similarity-guided local search can further reduce the data size
% to about 12.05\% of original size, namely it delivers an additional 12.09\% reduction.
% The PDS-based global duplicate detection with $\sigma=2\% $
% can reduce the size further to 8.6\% of original size, namely it 
% delivers an additional 3.45\% reduction.

In summary, our experiments show that
segment-level version detection 
reduces the data size to about 24.14\% of original data, 
which is a 75.86\% reduction. Namely 10TB snapshot data per machine is reduced to 2.414TB.
Similarity-guided local search can further reduce the data size
to about 1.205T, which is  12.05\% of original. Thus it delivers a 50.08\% reduction after the version-based
 deduplication.
The popularity-guided global deduplication with $\sigma=2\% $
reduces the data further to 860GB, namely 8.6\% of the original size. 
So it provides additional 28.63\% reduction. 
The overall memory usage of VC for each physical machine is very small, which is insignificant to other 
hosted cloud services.  In comparison, the 2.4GB per-machine memory usage of SRB is very visible 
to other services.
% even each physical machine in the production environment has 48GB memory.

@@

 \subsection{Effectiveness of Approximate Deletion}
\label{sect:evaldel}
\input{paper_eval_del}
\comments{
 \begin{figure}
\vspace{-0.1in}
     \centering
     \includegraphics[width=3in]{figures/leakage}
     \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}
     \label{fig:leakage}
 \end{figure}
}
\begin{table}
\centering
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline
Del. step   &     1 &  3  & 5 & 7  & 9 \\ 
\hline   
     Estimated& .02\% & .06\% & .10\%& .14\% & .18\%\\ 
\hline   
     Measured & .01\% & .055\% & .09\% & .12\% & .15\% \\
\hline   
    \end{tabular}
     \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}
     \label{tab:leakage}
\end{table}

@@

\comments{
The space cost for each snapshot deletion is insignificant.
Leakage repair for each VM needs less than 85MB of memory
considering each reference consumes 8 bytes plus  1 mark bit and  
each VM snapshot has 40GB backup data with about 10 million chunks. 
This VM-specific leakage  repair takes  less than half an hour for each VM. 
}
%when disk bandwidth is controlled to 50MB/s. 
%When using the traditional mark-and-sweep~\cite{Guo2011,Fabiano2013} in VO for 2500 VMs, 
%a total of 212GB memory
%space on 100 node is accessed for processing each VM and each machine requires 2.12GB.
%To control the garbage growth, such a process needs to be conducted much more frequently than our
%VM-centric leakage repair.

>>>>

\comments{
%old table, delete 4%
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline 
&
     \multicolumn{4}{|c|}{VC}  & VO \\ \hline
&
     2\%PDS  &  No PDS &2\%PDS     & 4\%PDS & SRB  \\ 
&     no-simi&   &&  &    \\ \hline
Dedup &     94.31\%& 93.02\%  & 96.01\% & 96.58\% & 97.86\% \\ \hline
Mem(MB) &     108&  46 & 118  & 190 & 2400 \\ \hline
    \end{tabular}
}
\begin{table}[htb]
\centering
    \begin{tabular}{|c|c|c|c|c|}
    \hline 
&
     \multicolumn{3}{|c|}{VC}  & VO \\ \hline
&       No PDS & No PDS &  2\%PDS     &   SRB  \\ 
&       no simi &simi   &  simi    &\\ \hline
Dedup & 75.86\%    &87.91\%  & 96.01\%   & 97.86\% \\ 
Efficiency & &           &       &                 \\    \hline 
Memory &     N/A&   10MB & 118MB  & 2.4GB \\ 
per-machine & &     &   &    \\ \hline
    \end{tabular}
    \caption{Deduplication efficiency and per-machine memory usage for different VC settings and
        SRB.}
    \label{tab:efficiency-comparison}
\end{table}

Table~\ref{tab:efficiency-comparison} shows the deduplication efficiency and per-machine memory usage for SRB and VC with different 
settings.
% <<<<<<< HEAD
% Our deduplication efficiency is defined as the percent of duplicate chunks
% which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
% The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
% is defined in Table~\ref{tab:symbol}. 
% =======
Deduplication efficiency is defined as the percent of duplicate 
chunks removed, comparing to a perfect scheme which detects and removes  all duplicates. 
% so only global perfect deduplication can have 100\% efficiency.
% We also compare several PDS sizes chosen for VC.
%(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
Notice $\sigma$ is the percentage of unique chunks selected in PDS.
With $\sigma =2\%$, Column 4 shows its 
%memory usage for PDS index lookup per machine is about 100MB per machine and  the 
deduplication efficiency can 
reach over 96\%. 
%When $\sigma=4\%$, Column 4 shows that the deduplication efficiency can reach 96.6\% while 
%more index space is allocated  per machine for  PDS fingerprint lookup.
The loss of efficiency in VC is caused by the restriction of the physical memory available
in the cluster for fast in-memory PDS index lookup. 
Memory usage per machine is low because each machine only hosts $1/p$  of  index for PDS 
plus some buffer space where $p$ is the number of physical machines. 
%In the extreme case if we put all the fingerprint into PDS 
%index ($\sigma=100\%$) then VC will have 100\% efficiency.
SRB in Column 5 can deliver up to 97.86\% deduplication efficiency, which is slightly better than VC.
Thus this represents a tradeoff as VC uses much less resource  and faster deletion.
%with a slight reduction in deduplication efficiency.
Memory usage per machine in SRB includes the Bloom filter space to access the on-disk index
and  cache for frequently or recently accessed chunk index.  
% SRB can deliver up to 97.935\% deduplication efficiency which is slightly better than VC.
% Thus this represents a tradeoff: VC provides better fault tolerance and fast
% approximate deletion with competitive (but slightly lower) deduplication
% efficiency.
% >>>>>>> 4dcd68612b052c0f890ed30361a9ed03771b5df1
%its loss of efficiency is caused by the routing of data chunks which restricts the search scope
%of duplicate detection.
%SRB provides slightly better deduplication efficiency than our VC approach, which we accept
%because we are rewarded by architecture-wise benefits such as fault-tolerance and fast 
%Though not our primary goal, this result does show that VC can remove competitive amount of duplicates.

Column 2 of Table~\ref{tab:efficiency-comparison} shows deduplication efficiency of VC without 
using PDS and local similarity search.
It just relies on the file segment dirty bits maintained in the Alibaba  virtual machine platform.
Thus there is no memory cost (marked as N/A).
Thus segment-level version detection 
reduces the data size to about 24.14\% of original data, 
which is a 75.86\% reduction. Namely 10TB snapshot data per machine is reduced to 2.414TB.
%Column 3 shows that with local similarity search,
%deduplication efficiency achieves 93\%.
% and  missed duplicates take  up-to  3.56\% of the original space, which
%is about 356GB per physical machine. 
Column 3 shows the deduplication result with similarity-guided local.
It  can further reduce the data size
to about 1.205T, which is  12.05\% of original. Thus it delivers a 50.08\% reduction after the version-based
deduplication.
The popularity-guided global deduplication with $\sigma=2\% $
reduces the data further to 860GB, namely 8.6\% of the original size. 
So it provides additional 28.63\% reduction. 
The overall memory usage of VC for each physical machine is very small, which is insignificant to other 
hosted cloud services.  In comparison, the 2.4GB per-machine memory usage of SRB is very visible 
to other services.

%There is a big efficiency drop in this curve when the number of VMs is about 30.

We explain why similarity-guided local search provides such an improvement as follows.
%Without this (i.e. when we only 
There are VMs in which data  segments are moved to another location on disk, for example 
when a file is rewritten
rather than modified in place,  
and a dirty-bit or offset-only based detection would not be able to detect such a movement.
We have found that in
approximately 1/3 of the VMs in our dataset this movement happens frequently.
%Column 4 of Table~\ref{tab:efficiency-comparison} shows deduplication efficiency of VC which only uses
%the same offset in the parent segment to look for duplicates  but does not look for other potentially
%similar segments. 
Compared an approach in ~\cite{WeiZhangIEEE} which maintains additional offset dirty bits within each segment,
 local similarity-guided search adds additional  deduplication efficiency about 3\%,
which is a saving of 300GB per machine.
%from 94\% to over 96\%.
%That is one significant improvement compared to the work in 
%which uses the parent segment at the same offset to detect duplicates instead of similarity-guided search.
% In general, our experiments show that
% dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
% which leads about a 75.86\% reduction.
% Similarity-guided local search can further reduce the data size
% to about 12.05\% of original size, namely it delivers an additional 12.09\% reduction.
% The PDS-based global duplicate detection with $\sigma=2\% $
% can reduce the size further to 8.6\% of original size, namely it 
% delivers an additional 3.45\% reduction.

% even each physical machine in the production environment has 48GB memory.

@@

\comments{
 \subsection{Effectiveness of Approximate Deletion}
\label{sect:evaldel}
\input{paper_eval_del}
\comments{
 \begin{figure}
\vspace{-0.1in}
     \centering
     \includegraphics[width=3in]{figures/leakage}
     \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}
     \label{fig:leakage}
 \end{figure}
}
\begin{table}
\centering
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline
Del. step   &     1 &  3  & 5 & 7  & 9 \\ 
\hline   
     Estimated& .02\% & .06\% & .10\%& .14\% & .18\%\\ 
\hline   
     Measured & .01\% & .055\% & .09\% & .12\% & .15\% \\
\hline   
    \end{tabular}
     \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}
     \label{tab:leakage}
\end{table}

@@

}
\comments{
The space cost for each snapshot deletion is insignificant.
Leakage repair for each VM needs less than 85MB of memory
considering each reference consumes 8 bytes plus  1 mark bit and  
each VM snapshot has 40GB backup data with about 10 million chunks. 
This VM-specific leakage  repair takes  less than half an hour for each VM. 
}
%when disk bandwidth is controlled to 50MB/s. 
%When using the traditional mark-and-sweep~\cite{Guo2011,Fabiano2013} in VO for 2500 VMs, 
%a total of 212GB memory
%space on 100 node is accessed for processing each VM and each machine requires 2.12GB.
%To control the garbage growth, such a process needs to be conducted much more frequently than our
%VM-centric leakage repair.

### 2015-03-10 snapshot_system/mass_intro.tex
re

Our work  considers a backup service for converged cloud architectures
that is co-located with user VMs, sharing the cloud compute, network, and
storage resource with them.  
This paper extends our preliminary simulation study  in ~\cite{WeiZhangIEEE} to 
restrict the scope of cross-VM deduplication and simplify the deduplication process
by separating popular data chunks and presents the design and implementation of 
a VM-centric backup scheme.  
We term this approach {\em VM-centric} because the deduplication
algorithm considers VM boundaries in making its decisions as opposed to
treating all blocks as being equivalent within the storage system.
Our work focuses on a tradeoff that allows the sharing of only ``popular'' data blocks 
across virtual machines while using localized deduplication within each VM
to achieve both storage savings and fault isolation.
Another issue addressed is fault  isolation in a content sharing environment caused by deduplication.
One consequence of aggressive deduplication is the possible loss of failure
resilience.  If a shared block is lost, all files that
share that block are affected.  Our work is motivated by \cite{Reliability06} that provides more
replication for shared file system blocks and proposes VM-centric techniques.
to 
\comments{
Since the underlying storage file system block size is typically bigger than the average data chunk size
used for deduplication,  packaging
content from different VMs into the same file block  creates a ``false'' sharing that 
affects fault isolation;
}

The main contribution of this paper is
1) a similarity-guided local deduplication for
each VM to make the overall deduplication efficiency more competitive 
to a transitional deduplication scheme;
2) a VM-centric file block management to improve snapshot availability by
separating popular chunk replication and
packaging data chunks from the same VM into a file system block as much as possible; 
3) a design and implementation of a VM-centric  backup service to integrate and validate
the proposed techniques while imposing  little resource usage and  minimizing the impact on other collocated cloud services.
Our  experimental study compares  the VM-centric approach with the previous 
VM-oblivious approaches in terms of deduplication efficiency, resource usage,  and snapshot availability.
%Thus we improve  to avoid such VM-oblivious packaging.
%our approach uses a deduplication data chunk size that is smaller than a
%single file block and

>>>>

Our work  considers a backup service with source-side deduplication for converged cloud architectures
that is co-located with user VMs, sharing the cloud compute, network, and
storage resource with them.  
This paper extends our preliminary simulation study  in ~\cite{WeiZhangIEEE} to 
restrict the scope of cross-VM deduplication and simplify the deduplication process
by separating popular data chunks and presents the design and implementation of 
a VM-centric backup scheme.  
We term this approach {\em VM-centric} because the deduplication
algorithm considers VM boundaries in making its decisions as opposed to
treating all blocks as being equivalent within the storage system.
Our work focuses on a tradeoff that allows the sharing of only ``popular'' data blocks 
across virtual machines while using localized deduplication within each VM
to achieve both storage savings and fault isolation.
Another issue addressed is fault  isolation in a content sharing environment caused by deduplication.
One consequence of aggressive deduplication is the possible loss of failure
resilience.  If a shared block is lost, all files that
share that block are affected~\cite{Reliability06} and  our work is motivated by this
and develops VM-centric fault isolation techniques.
\comments{
Since the underlying storage file system block size is typically bigger than the average data chunk size
used for deduplication,  packaging
content from different VMs into the same file block  creates a ``false'' sharing that 
affects fault isolation;
}

The main contribution of this paper is
1) a similarity-guided local deduplication for
each VM to make the overall deduplication efficiency more competitive 
to a transitional deduplication scheme;
2) a VM-centric file block management to improve snapshot availability by
separating popular chunk replication and
packaging data chunks from the same VM into a file system block as much as possible; 
3) a design and implementation of a VM-centric  backup service to integrate and validate
the proposed techniques while imposing  little resource usage and  minimizing the impact on other 
collocated cloud services.We provide an analysis on the deduplication efficiency by using popular items
and also on fault isolation.
Our  experimental study compares  the VM-centric approach with the previous 
VM-oblivious approaches in terms of deduplication efficiency, resource usage,  and snapshot availability.
%Thus we improve  to avoid such VM-oblivious packaging.
%our approach uses a deduplication data chunk size that is smaller than a
%single file block and

### 2015-03-10 snapshot_system/temp.tex
re

\section{Impact of Top $k$ Value on Deduplication Efficiency}
\label{sect:dedupanalysis}

Choosing the top $k$ value  for the most popular chunks affects the deduplication efficiency.
We analyze this impact based on the characteristics  of the VM snapshot traces
studied from  application datasets.
A previous study shows that the popularity of data chunks after local deduplication follows 
a Zipf-like distribution\cite{Breslau1999a} and its
exponent $\alpha$ is ranged between 0.65  and  0.7~\cite{WeiZhangIEEE}. 
%Figure~\ref{fig:Datazipf} illustrates the Zipf-like distribution of chunk popularity.
Additional parameters used in this analysis are defined in Table~\ref{tab:symbol2}.

\begin{table}[htbp]
%\begin{table}[t]
\small
\centering
%\tabcolsep=0.11cm
\begin{tabular}{|p{1.0cm}|p{5.75cm}|}
\hline
$k$ &  the number of top most popular chunks selected for deduplication\\ 
\hline
$c$ &  the total amount of data chunks in a cluster of VMs\\ 
\hline
$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
\hline
$f_i$ &  the frequency for the $i$th most popular fingerprint\\
\hline
$\delta$ &  the percentage of duplicates detected in local deduplication\\
\hline
$\sigma$ & = percentage of unique data  belonging to  PDS\\
%\hline
%$V$ & the average number of VMs per machine\\
\hline
%$E_c, E_o$ & deduplication efficiency of VC and VO \\
%\hline
%$D$ & the amount of unique data on each machine\\
%\hline
%$s$ & the average data chunk size. Our setting is  4K.\\
%\hline
%$s$ & the average number of chunks per FSB\\
%\hline
%$m$ & memory size on each node used by VC\\ 
%\hline
%$E$ & the size of an popular data index entry\\
%\hline
%$N_1$, $N_2$ & the average no.  of non-PDS and PDS file blocks in a VM in VC\\
%\hline
%$N_o$, $V_o$ & the average no.  of file blocks  in a VM and the average no. of VMs shared by a file system block in VO\\
%\hline
%A(r) & availability of a file block with $r$ replicas and $d$ failed physical machines\\
%\hline
\end{tabular}
\caption{Parameters for modeling deduplication.}
%\caption{Parameters for modeling deduplication with top $k$ popular chunks.}
\label{tab:symbol2}
\end{table}

%Table~\ref{tab:symbol} defines paramters $c$, $c_u$, $f_i$, and $\delta$ used below.
%let $c$ be the total number of data chunks. 
%$c_u$ be the total number of fingerprints 
%in the global index after complete deduplication, and
%$f_i$ be the frequency for the $i$th most popular fingerprint. 
By Zipf-like distribution, $f_i = {f_1}/{i^\alpha}.$
The total number of chunks in our backup storage which
has local duplicates excluded is $c (1-\delta)$, this can be represented
as the sum of each unique fingerprint times its frequency:
%Since $ \sum_{i=1}^{c_u}f_i = c (1-\delta)$,
\[
f_1 \sum_{i=1}^{c_u}\frac{1}{i^\alpha} = c (1-\delta).
\]
Given $\alpha <1$, $f_1$ can be approximated with integration:
%\begin{equation}
\[
f_1=\frac{c(1-\alpha)(1-\delta)}{c_u^{1-\alpha}}.
\]
%\end{equation}

Thus putting the $k$ most popular fingerprints into PDS index can remove the following number of chunks during global 
deduplication:
\[
f_1 \sum_{i=1}^{k}\frac{1}{i^\alpha} \approx  
f_1 \int_{1}^{k}\frac{1}{x^\alpha} dx  \approx  f_1\frac{  k^{1-\alpha}} {1-\alpha}
=c(1-\delta) \sigma^{1-\alpha}.
\]

Deduplication efficiency of the VC approach using top $k$ popular chunks
is the percentage of duplicates that can be detected:  
\begin{equation}
\label{eq:dedupeff}
%\begin{split}
%e_k &= 
E_c=\frac{ c\delta + c(1-\delta) \sigma^{1-\alpha}}
{c  - c_u }.\\
%\end{split}
\end{equation}

% After the global deduplication, the number of remaining chunks is:
% \[
% c-E(c-c_u)
% \]

We store the PDS index using a distributed shared memory hash table such as Memcached
and allocate a fixed percentage of memory space per physical machine for top $k$ popular items.
As the number of physical machines ($p$) increases,
the entire cloud cluster can host more VMs; however,  ratio $\sigma$ which is $k/c_u$ remains
a constant because each physical machine on average still hosts a fixed constant number of 
VMs. Then the overall deduplication efficiency of VC defined in Formula~\ref{eq:dedupeff}
remains constant.
Thus the deduplication efficiency is stable  as $p$ increases as long as $\sigma$  is a constant.

\begin{figure}[htbp]
\vspace{2em}

  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={PDS Coverage},
            width=\linewidth,
            height=0.6\linewidth,
            cycle multi list={
                mline\nextlist
                [3 of]mmark*\nextlist
            },
            %cycle list name=mcolor,
            xlabel={Total num. chunks stored (in billions)},
            ylabel={PDS Coverage (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            %legend pos=outer north east,
            legend columns=2,
            legend style={
                at={(0.5,-0.30)},
            anchor=north},
            ]
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A1] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A2] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A4] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T1] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T2] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T4] {figures/cds_coverage.txt};
            \legend{Measured ($\sigma=1\%$),Measured ($\sigma=2\%$),Measured ($\sigma=4\%$),Predicted ($\sigma=1\%$),Predicted ($\sigma=2\%$),Predicted ($\sigma=4\%$)};
            \end{axis}
    \end{tikzpicture}
  \caption{Predicted vs. actual PDS coverage as data size increases.}
  \label{fig:cds-coverage}
\end{figure}
Ratio $\sigma^{1-\alpha}$ represents the percentage of the remaining
chunks detected as duplicates in global deduplication due to PDS.
We call this PDS coverage.
Figure~\ref{fig:cds-coverage} shows predicted PDS coverage using $\sigma^{1-\alpha}$ when $\alpha$ is fixed at
0.65 and measured PDS coverage in our test dataset.
$\sigma=2\%$ represents memory usage of approximately 100MB memory per machine for the PDS.
While the predicted value remains flat, measured PDS coverage increases as more VMs are involved.
This is because the actual $\alpha$ value increases with the data size.
%Then  PDS coverage PDS increases as more VMs are involved.

>>>>

Additional parameters used in this analysis are defined in Table~\ref{tab:symbol2}.

\begin{table}[htbp]
%\begin{table}[t]
\small
\centering
%\tabcolsep=0.11cm
\begin{tabular}{|p{1.0cm}|p{5.75cm}|}
\hline
$k$ &  the number of top most popular chunks selected for deduplication\\ 
\hline
$c$ &  the total amount of data chunks in a cluster of VMs\\ 
\hline
$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
\hline
$f_i$ &  the frequency for the $i$th most popular fingerprint\\
\hline
$\delta$ &  the percentage of duplicates detected in local deduplication\\
\hline
$\sigma$ & = percentage of unique data  belonging to  PDS\\
%\hline
%$V$ & the average number of VMs per machine\\
\hline
%$E_c, E_o$ & deduplication efficiency of VC and VO \\
%\hline
%$D$ & the amount of unique data on each machine\\
%\hline
%$s$ & the average data chunk size. Our setting is  4K.\\
%\hline
%$s$ & the average number of chunks per FSB\\
%\hline
%$m$ & memory size on each node used by VC\\ 
%\hline
%$E$ & the size of an popular data index entry\\
%\hline
%$N_1$, $N_2$ & the average no.  of non-PDS and PDS file blocks in a VM in VC\\
%\hline
%$N_o$, $V_o$ & the average no.  of file blocks  in a VM and the average no. of VMs shared by a file system block in VO\\
%\hline
%A(r) & availability of a file block with $r$ replicas and $d$ failed physical machines\\
\hline
\end{tabular}
\caption{Parameters for modeling deduplication with top $k$ popular chunks.}
\label{tab:symbol}
\end{table}
